G\"{o}del's Ontological Proof of God's Existence (Draft)

### 2013-08-18 Abstract/GodProof-Abstract.tex
Make the numbering of axioms, definitions and lemmas agree between abstract and natural deduction formalization

\begin{align}
& \text{Any property necessarily implied by a positive property is positive:} \notag \\
& \quad \forall P \forall Q (pos\,P \wedge (\Box \forall x (P\,x \Rightarrow Q\,x)) \Rightarrow pos\,Q) \tag{A1} \\
& \text{A property is positive if and only if its negation is not positive:} \notag \\
& \quad \forall P (pos\,P \Leftrightarrow \neg (pos\,\neg P)) \tag{A2} \\
& \text{The property of being God-like is positive:} \notag \\
& \quad pos\,god \tag{A3} \\
& \text{Positive properties are necessarily positive:} \notag \\
& \quad \forall P (pos\,P \Rightarrow \Box (pos\,P))\tag{A4} \\
& \text{Necessary existence is a positive property:} \notag \\
& \quad pos\,nec\_exists \tag{A5} \\
& \text{x is God-like if and only if x has every positive property:} \notag \\
& \quad god\,x := \forall P (pos\,P \Rightarrow P x) \tag{D1} \\
& \parbox[c][2em][c]{0.8\textwidth}{A property P is an essence of x if and only if P is a property of x and every property Q that x has is necessarily implied by P:}\notag \\
& \quad ess\,P\,x := P\,x \wedge \forall Q (Q\,x \Rightarrow \Box (\forall y (P\,y \Rightarrow Q\,y))) \tag{D2} 
\end{align}

@@

\item[(A4)] positive properties are necessarily positive; 
\item[(A5)] necessary existence is a positive property.
\item[(D1)] x is God-like if and only if x has every positive property, 
\item[(D2)] a property P is an essence of x if and only if P is a property of x and every property Q that x has is necessarily implied by P, 
\item[(D3)] x necessarily exists if and only if every essence of x is necessarily exemplified.
\end{description}

>>>>

\begin{align}
& \text{Any property necessarily implied by a positive property is positive:} \notag \\
& \quad \forall P \forall Q (pos\,P \wedge (\Box \forall x (P\,x \Rightarrow Q\,x)) \Rightarrow pos\,Q) \tag{A1} \\
& \text{A property is positive if and only if its negation is not positive:} \notag \\
& \quad \forall P (pos\,P \Leftrightarrow \neg (pos\,\neg P)) \tag{A2} \\
& \text{The property of being God-like is positive:} \notag \\
& \quad pos\,god \tag{A3} \\
& \text{Positive properties are necessarily positive:} \notag \\
& \quad \forall P (pos\,P \Rightarrow \Box (pos\,P))\tag{A4} \\
& \text{Necessary existence is a positive property:} \notag \\
& \quad pos\,nec\_exists \tag{A5} \\
& \parbox[c][2em][c]{0.8\textwidth}{A property P is an essence of x if and only if P is a property of x and every property Q that x has is necessarily implied by P:}\notag \\
& \quad ess\,P\,x := P\,x \wedge \forall Q (Q\,x \Rightarrow \Box (\forall y (P\,y \Rightarrow Q\,y))) \tag{D1} \\
& \text{x is God-like if and only if x has every positive property:} \notag \\
& \quad god\,x := \forall P (pos\,P \Rightarrow P x) \tag{D2}
\end{align}

@@

\item[(A4)] positive properties are necessarily positive; 
\item[(A5)] necessary existence is a positive property.
\item[(D1)] a property P is an essence of x if and only if P is a property of x and every property Q that x has is necessarily implied by P, 
\item[(D2)] x is God-like if and only if x has every positive property, 
\item[(D3)] x necessarily exists if and only if every essence of x is necessarily exemplified.
\end{description}

### 2013-08-18 Natural Deduction/GodProof-ND.tex
Make the numbering of axioms, definitions and lemmas agree between abstract and natural deduction formalization

\title{G\"{o}del's Ontological Proof of God's Existence }

@@

\textbf{Axioms:}
\begin{itemize}
\item \textbf{(1)} Properties necessarily entailed by \emph{positive} properties are also positive:
$$
\all \varphi. \all \psi.[(P(\varphi) \wedge \nec \all x.[\varphi(x) \imp \psi(x)]) \imp P(\psi)]
$$
%
\item \textbf{(2)} A property's negation is positive iff the property is not positive:
$$
\all \varphi. [P(\neg \varphi) \biimp \neg P(\varphi)]
$$
\end{itemize}

\noindent
\textbf{Theorem 1:} Positive properties possibly have a witness:
$$
\all \varphi. [P(\varphi) \imp \pos \ex x.\varphi(x)]
$$

@@

\textbf{Axioms:}
\begin{itemize}
\item \textbf{(3)} Being God is a positive property:
$$
P(G)
$$
\end{itemize}

\noindent
\textbf{Theorem 2:} It is possible that a God exists:
$$
\pos \ex x. G(x)
$$

@@

\textbf{Definitions:}
\begin{itemize}
\item A property is \emph{essential} for an individual if and only if it holds for that inidividual and necessarily entails every other property that holds for that individual: $\ess{\varphi}{x} \biimp \varphi(x) \wedge \all \psi. (\psi(x) \imp \nec \all x. (\varphi(x) \imp \psi(x)))$
\end{itemize}

\noindent
\textbf{Axioms:}
\begin{itemize}
\item \textbf{(4)} Positive properties are necessarily positive:
$$
\all \varphi.[P(\varphi) \to \Box \; P(\varphi)]
$$
\end{itemize}

\noindent
\textbf{Theorem 3}: If an individual is a God, then being God is an essential property for that individual:
$$
\all y.[G(y) \imp \ess{G}{y}]
$$

@@

\textbf{Definitions:}
\begin{itemize}
\item An individual is a \emph{God} if and only if he possesses all positive properties:
$$
G(x) \biimp \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\item An individual \emph{necessarily exists} if and only if all its essential properties are necessarily witnessed:
$$
E(x) \biimp \all \varphi.[\ess{\varphi}{x} \imp \nec \ex x.\varphi(x)]
$$
\end{itemize}

\noindent
\textbf{Axioms:}
\begin{itemize}
\item \textbf{(5)} Necessary existence is a positive property:
$$
P(E)
$$
\end{itemize}

\noindent
\textbf{Theorem A:} If there is a God, then there necessarily exists a God:
$$
\ex z. G(z) \imp \nec \ex x. G(x)
$$

@@

\noindent
\textbf{Theorem 4:} The existence of a God is necessary:
$$
\nec \ex x. G(x)
$$

@@

\noindent
\textbf{Theorem:} There exists a God:
$$
\ex x. G(x)
$$

>>>>

\title{G\"{o}del's Ontological Proof of God's Existence (Draft)}

@@

\textbf{Axioms:}
\begin{itemize}
\item \textbf{(A1)} Properties necessarily entailed by \emph{positive} properties are also positive:
$$
\all \varphi. \all \psi.[(P(\varphi) \wedge \nec \all x.[\varphi(x) \imp \psi(x)]) \imp P(\psi)]
$$
%
\item \textbf{(A2)} A property's negation is positive iff the property is not positive:
$$
\all \varphi. [P(\neg \varphi) \biimp \neg P(\varphi)]
$$
\end{itemize}

\noindent
\textbf{Lemma 1:} Positive properties possibly have a witness:
$$
\all \varphi. [P(\varphi) \imp \pos \ex x.\varphi(x)]
$$

@@

\textbf{Axioms:}
\begin{itemize}
\item \textbf{(A3)} Being God is a positive property:
$$
P(G)
$$
\end{itemize}

\noindent
\textbf{Lemma 2:} It is possible that a God exists:
$$
\pos \ex x. G(x)
$$

@@

\textbf{Definitions:}
\begin{itemize}
\item \textbf{(D1)} A property is \emph{essential} for an individual if and only if it holds for that inidividual and necessarily entails every other property that holds for that individual: $\ess{\varphi}{x} \biimp \varphi(x) \wedge \all \psi. (\psi(x) \imp \nec \all x. (\varphi(x) \imp \psi(x)))$
\end{itemize}

\noindent
\textbf{Axioms:}
\begin{itemize}
\item \textbf{(A4)} Positive properties are necessarily positive:
$$
\all \varphi.[P(\varphi) \to \Box \; P(\varphi)]
$$
\end{itemize}

\noindent
\textbf{Lemma 3}: If an individual is a God, then being God is an essential property for that individual:
$$
\all y.[G(y) \imp \ess{G}{y}]
$$

@@

\textbf{Definitions:}
\begin{itemize}
\item \textbf{(D2)} An individual is a \emph{God} if and only if he possesses all positive properties:
$$
G(x) \biimp \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\item \textbf{(D3)} An individual \emph{necessarily exists} if and only if all its essential properties are necessarily witnessed:
$$
E(x) \biimp \all \varphi.[\ess{\varphi}{x} \imp \nec \ex x.\varphi(x)]
$$
\end{itemize}

\noindent
\textbf{Axioms:}
\begin{itemize}
\item \textbf{(A5)} Necessary existence is a positive property:
$$
P(E)
$$
\end{itemize}

\noindent
\textbf{Auxiliary Lemma:} If there is a God, then there necessarily exists a God:
$$
\ex z. G(z) \imp \nec \ex x. G(x)
$$

@@

\noindent
\textbf{Theorem:} The existence of a God is necessary:
$$
\nec \ex x. G(x)
$$

@@

\noindent
\textbf{Corollary:} There exists a God:
$$
\ex x. G(x)
$$
